---
output: github_document
---

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# rVMAP

The rVMAP package is intended to improve the efficiency and reproducibility of collaborations between [VUMC Department of Biostatistics](http://biostat.mc.vanderbilt.edu/) and the [Vanderbilt Memory and Alzheimer's Center](https://www.vumc.org/vmac/) for Vanderbilt Memory and Aging Project studies. rVMAP is intended for internal use and contains the following:

- functions that are commonly used in statistical analysis in VMAC research
- scripts that will help automate mundane tasks (e.g. quarterly data freeze and data merge)
- dot files to help ensure consistent environments across users and computers

## Installation

You can install rVMAP from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("liud4/rVMAP")
```

After installing the package, there will be a new R Markdown template for the data merge code in `File > New File > R Markdown > From Template > MAP Data: Merge, Derive, and Label`.
