---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# rVMAC

The rVMAC package is intended to improve the efficiency and reproducibility of collaborations between [VUMC Department of Biostatistics](http://biostat.mc.vanderbilt.edu/) and the [Vanderbilt Memory and Alzheimer's Center](https://www.vumc.org/vmac/). rVMAC is intended for internal use and contains the following:

- functions that are commonly used in statistical analysis in VMAC research
- scripts that will help automate mundane tasks (e.g. quarterly [data freeze](./demo/data-freeze.R) and [data merge](./demo/data-merge.nb.html))
- vesion-controlled snapshots of external packages to ensure consistency and reproducibility
- dot files to help ensure consistent environments across users and computers

## Installation

You can install rVMAC from github with:

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("prettynumbers/rVMAC")
```

<!-- ## Example -->

<!-- This is a basic example which shows you how to solve a common problem: -->

<!-- ```{r example} -->
<!-- ## basic example code -->
<!-- ``` -->
