---
title: "MAP Data: Merge, Derive, and Label"
subtitle: "Draft"
author:
- name: '[Omair A. Khan, MAS](omair.a.khan@vumc.org)'
- name: '[Dandan Liu, PhD](dandan.liu@vanderbilt.edu)'
date: "Created: 20180503 | Last Modified: `r format(Sys.time(), '%Y%m%d')`"
output:
  html_notebook:
    code_folding: hide
    theme: lumen
    number_sections: yes
    toc: yes
    toc_float:
      collapsed: yes
      smooth_scroll: true
---

<!-- ##%#########################################################%## -->
<!-- # Template: MAP Data: Merge, Derive, and Label                # -->
<!-- #                                                             # -->
<!-- # Description: This script is run quarterly to merge, derive, # -->
<!-- #   and label the MAP data. The script requires the VMACr     # -->
<!-- #   package. It is configured to optionally perform the data  # -->
<!-- #   freeze as well.                                           # -->
<!-- #                                                             # -->
<!-- # Status: Currently non-functional. This is a draft that      # -->
<!-- #    includes legacy code from L. Samuels that needs to be    # -->
<!-- #    modernized before it can be used. (20180507)             # -->
<!-- ##%#########################################################%## -->

<style type="text/css">
 #TOC{
   position:fixed;
   top:0;
   // left:0;
   right:0;
   margin: 32px 20px 20px 20px;
   z-index: 9;
   // display:none;
  }
  #toc-toggle{
    position:fixed;
    top:0;
    // left:0;
    right:0;
    margin: 5px 20px 5px 20px;
  }
  .col-md-3{
    width: 0%;
  }
  .col-md-9{
    width: 100%;
  }
  div.container-fluid.main-container{
    max-width:none;
    margin-left:0px;
    margin-right:none;
  }
  div.plot-container{
    margin-left:50px;
    margin-bottom:20px;
  }
  h1.title{
    max-width:950px;
  }
  li.tocify-item{
    text-indent:0px;
  }
  #toc-toggle{
    z-index:9;
  }
  .tocify-subheader, .tocify-item, .tocify, .list-group-item{
  font-size:12pt;
  }
</style>

<button id="toc-toggle" type="button" class="btn btn-default btn-xs code-folding-btn pull-right collapsed" onclick="toggletoc()"><span>Table of Contents (click to hide/show)</span></button>

<script>
function toggletoc(){
$("#TOC").toggle();
}
</script>

```{r setup, echo = TRUE, results = 'hide'}
# clear environment
rm(list = ls())
options(datadist = NULL)

packages <- Hmisc::Cs(
  knitr,
  dplyr,
  lubridate,
  tidyr,
  stringr,
  magrittr,
  daff,
  Hmisc,
  formattable,
  REDCapR,
  secret
)

load_pkg(packages)

##%######################################################%##
####                modifiable settings                 ####
# modify this variable as follows: quarterly scheduled merge = {TRUE}; off-cycle merge = {FALSE}
quarterly.download <- TRUE
# modify one of these variables to download data or specify a specific raw data file to merge
download.data <- FALSE
data.freeze.date <- "20180817" # in {yyyymmdd} format
# modify these variables to specify a specific data merge file to compare the new one with
last.data.download.date <- NULL
last.data.merge.date <- NULL
# last.data.merge.suffix <- NULL  # in d{yyyymmdd}_m{yyyymmdd} format
####                                                    ####
##%######################################################%##

#devtools::load_all()

# set timezone
Sys.setenv(TZ = 'US/Central')

# set seed
set.seed(20140728) # this number was set by L. Samuels in the previous version of this code

# Hmisc options
options(
  prType = 'html', 
  grType = 'plotly',
  digits = 6,
  contrasts = c("contr.treatment", "contr.treatment")
)

# define important directories
## base directories
box.dir  <- file.path("~", "box")
vmac.dir <- file.path(box.dir, "VMAC BIOSTAT")
func.dir <- useful.dir <- file.path(vmac.dir, "Useful Code")
## data directories
data.dir <- file.path(vmac.dir, "DATA", "MAP")
data.raw.dir <- ifelse(quarterly.download,
                       file.path(data.dir, "rawData"),
                       file.path(data.dir, "rawData", "temp"))
data.merge.dir <- file.path(data.dir, 'mergedData')
```

```{r finish-setup}
if (download.data == TRUE) {
  # specify data freeze date
  data.freeze.date <- format(Sys.time(), "%Y%m%d")
  # load raw data
  MAPfreeze.list <- data_freeze(quarterly.download = quarterly.download, save = TRUE)
} else if (download.data == FALSE & is.null(data.freeze.date)) {
  # get path to most recent REDCap freeze
  data.freeze.file <- file.info(
    list.files(
      path = data.raw.dir, 
      pattern = "MAPfreeze_\\d{8}.rds",
      full.names = T
    )
  ) %>%
    tibble::rownames_to_column(., var = "path") %>%
    arrange(desc(mtime)) %>% 
    filter(row_number() == 1) %>%
    pull(1)
  # extract data freeze date
  data.freeze.date <- stringr::str_extract(data.freeze.file, "\\d{8}")
  # load raw data
  MAPfreeze.list <- readRDS(data.freeze.file)
} else if (download.data == FALSE & !is.null(data.freeze.date)) {
  # data freeze date is user specified
  # load raw data
  MAPfreeze.list <- readRDS(
    file.path(
      data.raw.dir,
      paste0(
        "MAPfreeze_", 
        data.freeze.date, 
        ".rds"
      )
    )
  )
} else {
  stop("Either `download.data` or `data.freeze.date` must be specified as TRUE or FALSE and a 8 digit yyyymmdd, respectively.")
}

# define paths for saving current merged files
data.merge.date <- format(Sys.time(), "%Y%m%d")
current.data.merge.suffix <- paste0("_d", data.freeze.date, "_m", data.merge.date)
# OAK 20180507 later, combine the fm and bh files into one taller dataset where nrows = n(map.id) + 25  and ncol = ncol(merged.data) + 1  # 25 is the number of breath hold participants and the extra column is whether the data is BH or not
data.merge.fm.file <- file.path(
  data.merge.dir, 
  paste0("MAP_fm_d", data.freeze.date, "_m", data.merge.date)
)
data.merge.bh.file <- file.path(
  data.merge.dir, 
  paste0("MAP_bh_d", data.freeze.date, "_m", data.merge.date)
)

if (!is.null(last.data.download.date) & is.null(last.data.merge.date)) {
  error("Please specify the last data merge date.")
} else if (is.null(last.data.download.date) & !is.null(last.data.merge.date)) {
  error("Please specify the last data download date.")
} else if (is.null(last.data.download.date) & is.null(last.data.merge.date)) {
  # extact date of previous data merge
  last.data.merge.suffix <- file.info(
    list.files(
      path = data.merge.dir,
      pattern = "MAP\\_bh\\_d\\d{8}\\_m\\d{8}.rds",
      full.names = T
    )
  ) %>%
    tibble::rownames_to_column(., var = "path") %>%
    arrange(desc(mtime)) %>%
    filter(row_number() == 1) %>%
    pull(1) %>%
    stringr::str_extract("(?<=(MAP\\_bh\\_))d\\d{8}\\_m\\d{8}")
} else {
  last.data.merge.suffix <- paste0("d_", last.data.download.date, "_m_", last.data.merge.date)
}

# define path to previous merged datasets
last.data.merge.fm.file <- file.path(
  data.merge.dir, 
  paste0("MAP_fm_", last.data.merge.date)
)
last.data.merge.bh.file <- file.path(
  data.merge.dir, 
  paste0("MAP_bh_", last.data.merge.date)
)
```

# Overview

TODO: Explain what the different variables are here.

## Epoch Independent

TODO: Add description for what Epoch Independent means.

```{r list-projects-epoch0}
list(
  project = MAPfreeze.list[["epoch_0"]][["project"]],
  shortname = MAPfreeze.list[["epoch_0"]][["shortname"]]
) %>% rbind.data.frame()
```

## Epoch 1

```{r list-projects-epoch1}
list(
  project = MAPfreeze.list[["epoch_1"]][["project"]],
  shortname = MAPfreeze.list[["epoch_1"]][["shortname"]]
) %>% rbind.data.frame()
```

## Epoch 2

```{r list-projects-epoch2}
list(
  project = MAPfreeze.list[["epoch_2"]][["project"]],
  shortname = MAPfreeze.list[["epoch_2"]][["shortname"]]
) %>% rbind.data.frame()
```

## Epoch 3

```{r list-projects-epoch3}
list(
  project = MAPfreeze.list[["epoch_3"]][["project"]],
  shortname = MAPfreeze.list[["epoch_3"]][["shortname"]]
) %>% rbind.data.frame()
```

## Epoch 4

```{r list-projects-epoch4}
list(
  project = MAPfreeze.list[["epoch_4"]][["project"]],
  shortname = MAPfreeze.list[["epoch_4"]][["shortname"]]
) %>% rbind.data.frame()
```

# Data Merge

TODO: Explain

## Merge within Epoch 1

We will begin by merging the following data sets within Epoch 1:

TODO: 

```{r merge-within-epoch1}
epoch_1_merge.df <- mergeWithinEpoch(
  epoch = 1,
  main = MAPfreeze.list$epoch_1$data$main,
  abp = MAPfreeze.list$epoch_1$data$abp.static,
  biomarkers = MAPfreeze.list$epoch_1$data$biomarkers,
  auto3T = MAPfreeze.list$epoch_1$data$auto3T,
  auto3TBH = MAPfreeze.list$epoch_1$data$auto3T.bh,
  man3T = MAPfreeze.list$epoch_1$data$man3T,
  man3TBH = MAPfreeze.list$epoch_1$data$man3T.bh,
  qmass = MAPfreeze.list$epoch_1$data$cardiac.mri,
  addendum = MAPfreeze.list$epoch_1$data$addendum,
  csf = MAPfreeze.list$epoch_1$data$csf,
  srt = MAPfreeze.list$epoch_1$data$srt.static
)
```

## Merge within Epoch 2

Next, we will merge the following data sets within Epoch 2:

TODO: 

```{r merge-within-epoch2}
epoch_2_merge.df <- mergeWithinEpoch(
  epoch = 2,
  main = MAPfreeze.list$epoch_2$data$main,
  # abp = MAPfreeze.list$epoch_2$data$abp.static,
  biomarkers = MAPfreeze.list$epoch_2$data$biomarkers,
  auto3T = MAPfreeze.list$epoch_2$data$auto3T,
  # auto3TBH = MAPfreeze.list$epoch_2$data$auto3T.bh,
  man3T = MAPfreeze.list$epoch_2$data$man3T,
  # man3TBH = MAPfreeze.list$epoch_2$data$man3T.bh,
  qmass = MAPfreeze.list$epoch_2$data$cardiac.mri,
  # addendum = MAPfreeze.list$epoch_2$data$addendum,
  csf = MAPfreeze.list$epoch_2$data$csf
  # srt = MAPfreeze.list$epoch_2$data$srt.static
)
```

## Merge within Epoch 3

We will repeat this process for the following data sets within Epoch 3:

TODO: 

```{r merge-within-epoch3}
epoch_3_merge.df <- mergeWithinEpoch(
  epoch = 3,
  main = MAPfreeze.list$epoch_3$data$main,
  # abp = MAPfreeze.list$epoch_3$data$abp.static,
  biomarkers = MAPfreeze.list$epoch_3$data$biomarkers,
  auto3T = MAPfreeze.list$epoch_3$data$auto3T,
  # auto3TBH = MAPfreeze.list$epoch_3$data$auto3T.bh,
  man3T = MAPfreeze.list$epoch_3$data$man3T,
  # man3TBH = MAPfreeze.list$epoch_3$data$man3T.bh,
  # qmass = MAPfreeze.list$epoch_3$data$cardiac.mri,
  # addendum = MAPfreeze.list$epoch_3$data$addendum,
  csf = MAPfreeze.list$epoch_3$data$csf
  # srt = MAPfreeze.list$epoch_3$data$srt.static
)
```

## Merge within Epoch 4

We will repeat this process for the following data sets within Epoch 4:

TODO: 

```{r merge-within-epoch3}
epoch_4_merge.df <- mergeWithinEpoch(
  epoch = 4,
  main = MAPfreeze.list$epoch_4$data$main,
  # abp = MAPfreeze.list$epoch_4$data$abp.static,
  # biomarkers = MAPfreeze.list$epoch_4$data$biomarkers,
  auto3T = MAPfreeze.list$epoch_4$data$auto3T,
  # auto3TBH = MAPfreeze.list$epoch_4$data$auto3T.bh,
  man3T = MAPfreeze.list$epoch_4$data$man3T,
  # man3TBH = MAPfreeze.list$epoch_4$data$man3T.bh,
  # qmass = MAPfreeze.list$epoch_4$data$cardiac.mri,
  # addendum = MAPfreeze.list$epoch_4$data$addendum,
  csf = MAPfreeze.list$epoch_4$data$csf
  # srt = MAPfreeze.list$epoch_4$data$srt.static
)
```

## Merge across all epochs

In this section, we will compare and stack the merged Epoch data.

### Compare and stack: Epoch 2 with Epoch 1

Here we refer to the Epoch 2 data as "new" and the previous epochs (Epoch 1) as "old."

```{r compare-epoch1-epoch2}
compareVarnames(newdat = epoch_2_merge.df, olddat = epoch_1_merge.df)
compareIDs(newdat = epoch_2_merge.df, olddat = epoch_1_merge.df)
compareFactors(newdat = epoch_2_merge.df, olddat = epoch_1_merge.df)
```

```{r coerce-stack-epoch1-epoch2}
merged.df <- coerce_and_stack(newdat = epoch_2_merge.df, olddat = epoch_1_merge.df)

# med16_dose, med19_dose, med20_dose, famhx01_age_inf, bld_c_alt, bld_c_igg, bld_c_coag, bld_c_tsh, abp_date, np_mc_kaplan_ss, biomarkers_tau_plasma, csf_gap43, eve_session_id_auto3T, asl_session_id_auto3T, veasl_session_id_auto3T

# merged.df[, Cs(med16_dose, med19_dose, med20_dose, famhx01_age_inf, bld_c_alt, bld_c_igg, bld_c_coag, bld_c_tsh, abp_date, np_mc_kaplan_ss, biomarkers_tau_plasma, csf_gap43, eve_session_id_auto3T, asl_session_id_auto3T, veasl_session_id_auto3T)] <- lapply(merged.df[, Cs(med16_dose, med19_dose, med20_dose, famhx01_age_inf, bld_c_alt, bld_c_igg, bld_c_coag, bld_c_tsh, abp_date, np_mc_kaplan_ss, biomarkers_tau_plasma, csf_gap43, eve_session_id_auto3T, asl_session_id_auto3T, veasl_session_id_auto3T)], as.numeric)
```

### Compare and stack: Epoch 3 with Epochs 1 and 2

Here we refer to the Epoch 3 data as "new" and the previous epochs (Epochs 1 and 2) as "old."

```{r compare-epoch12-epoch3}
compareVarnames(newdat = epoch_3_merge.df, olddat = merged.df)
compareIDs(newdat = epoch_3_merge.df, olddat = merged.df)
compareFactors(newdat = epoch_3_merge.df, olddat = merged.df)
```

```{r coerce-stack-epoch12-epoch3}
merged.df <- coerce_and_stack(newdat = epoch_3_merge.df, olddat = merged.df)

# med16_dose, med17_dose, bld_c_alt, bld_c_tsh, bld_c_insulin, cmr_findings_pulse, cmr_findings_dbp, freesurfer_2005_session_id_auto3T, freesurfer_2009_session_id_auto3T, freesurfer_lobes_session_id_auto3T, freesurfer_hippocampal_subfields_session_id_auto3T, freesurfer_brain_volume_session_id_auto3T, ma_session_id_auto3T, wml_session_id_auto3T, vbmqa_session_id_auto3T, fslfirst_session_id_auto3T

# merged.df[, Cs(med16_dose, med17_dose, bld_c_alt, bld_c_tsh, bld_c_insulin, cmr_findings_pulse, cmr_findings_dbp, freesurfer_2005_session_id_auto3T, freesurfer_2009_session_id_auto3T, freesurfer_lobes_session_id_auto3T, freesurfer_hippocampal_subfields_session_id_auto3T, freesurfer_brain_volume_session_id_auto3T, ma_session_id_auto3T, wml_session_id_auto3T, vbmqa_session_id_auto3T, fslfirst_session_id_auto3T)] <- lapply(merged.df[, Cs(med16_dose, med17_dose, bld_c_alt, bld_c_tsh, bld_c_insulin, cmr_findings_pulse, cmr_findings_dbp, freesurfer_2005_session_id_auto3T, freesurfer_2009_session_id_auto3T, freesurfer_lobes_session_id_auto3T, freesurfer_hippocampal_subfields_session_id_auto3T, freesurfer_brain_volume_session_id_auto3T, ma_session_id_auto3T, wml_session_id_auto3T, vbmqa_session_id_auto3T, fslfirst_session_id_auto3T)], as.numeric)
```

### Compare and stack: Epoch 4 with Epochs 1, 2, and 3

Here we refer to the Epoch 4 data as "new" and the previous epochs (Epochs 1, 2, and 3) as "old."

```{r compare-epoch123-epoch4}
compareVarnames(newdat = epoch_4_merge.df, olddat = merged.df)
compareIDs(newdat = epoch_4_merge.df, olddat = merged.df)
compareFactors(newdat = epoch_4_merge.df, olddat = merged.df)
```


```{r coerce-stack-epoch123-epoch4}
merged.df <- coerce_and_stack(newdat = epoch_4_merge.df, olddat = merged.df)

# med04_dose, med08_dose, med09_dose, med10_dose, med11_dose, med12_dose, med14_dose, med15_dose, mhx_other_add, mlta01, famhx02_age_ptp, famhx01_age_inf, bld_c_alt, bld_c_igm, echo_comments, cmr_findings_dbp, np_pvltrecog_falsepos, np_3digits_span, np_3digits_intrus, np_3digits_cap, np_3digits_frontal, np_3digits_errors, np_3digits_btcfor, np_3digits_btcback

merged.df[, c("asl_session_id_auto3T", "biomarkers_tau_plasma", "bld_c_alt", 
"bld_c_coag", "bld_c_igg", "bld_c_igm", "bld_c_insulin", "bld_c_tsh", 
"cmr_findings_dbp", "cmr_findings_pulse", "csf_gap43", "eve_session_id_auto3T", 
"famhx01_age_inf", "famhx02_age_ptp", "freesurfer_2005_session_id_auto3T", 
"freesurfer_2009_session_id_auto3T", "freesurfer_brain_volume_session_id_auto3T", 
"freesurfer_hippocampal_subfields_session_id_auto3T", "freesurfer_lobes_session_id_auto3T", 
"fslfirst_session_id_auto3T", "ma_session_id_auto3T", "mlta01", 
"np_3digits_btcback", "np_3digits_btcfor", "np_3digits_cap", 
"np_3digits_errors", "np_3digits_frontal", "np_3digits_intrus", 
"np_3digits_span", "np_mc_kaplan_ss", "np_pvltrecog_falsepos", 
"vbmqa_session_id_auto3T", "veasl_session_id_auto3T", "wml_session_id_auto3T"
)] <- lapply(merged.df[, c("asl_session_id_auto3T", "biomarkers_tau_plasma", "bld_c_alt", 
"bld_c_coag", "bld_c_igg", "bld_c_igm", "bld_c_insulin", "bld_c_tsh", 
"cmr_findings_dbp", "cmr_findings_pulse", "csf_gap43", "eve_session_id_auto3T", 
"famhx01_age_inf", "famhx02_age_ptp", "freesurfer_2005_session_id_auto3T", 
"freesurfer_2009_session_id_auto3T", "freesurfer_brain_volume_session_id_auto3T", 
"freesurfer_hippocampal_subfields_session_id_auto3T", "freesurfer_lobes_session_id_auto3T", 
"fslfirst_session_id_auto3T", "ma_session_id_auto3T", "mlta01", 
"np_3digits_btcback", "np_3digits_btcfor", "np_3digits_cap", 
"np_3digits_errors", "np_3digits_frontal", "np_3digits_intrus", 
"np_3digits_span", "np_mc_kaplan_ss", "np_pvltrecog_falsepos", 
"vbmqa_session_id_auto3T", "veasl_session_id_auto3T", "wml_session_id_auto3T"
)], as.numeric)

###

names(merged.df) <- gsub("\\_", "\\.", names(merged.df))
merged.df.bkup <- merged.df
```

## Merge Epoch independent data

TODO: Explain.

### Add ABPM consent data

```{r}
tracking.static.df <- MAPfreeze.list$epoch_0$data$tracking.static %>%
  select(
    map_id, elig_visit_consent_abpm, elig_visit_consent_lp, elig_visit_consent_lp_ineligible
  ) %>%
  format_id(.) %>%
  do(
    fix_names(.)
  )

check_shared_vars(merged.df, tracking.static.df, 'map.id')

merged.df %<>% left_join(
  tracking.static.df,
  by = "map.id"
) %>% 
  mutate(
    abp.consent = ifelse(epoch == 1, elig.visit.consent.abpm, NA),
    abp.consent.factor = factor(abp.consent, levels = c(1, 0), labels = c("Yes", "No")) 
  )
```

### Add post-fixed eligibility data

```{r}
eligibility.static.df <- MAPfreeze.list$epoch_0$data$eligibility.static %>%
  format_id() %>%
  do(
    fix_names(.)
  ) %>%
  modify_eligibility()

check_shared_vars(merged.df, eligibility.static.df, 'map.id')

merged.df %<>% left_join(
  eligibility.static.df,
  by = "map.id"
) 
```

## Apply labels to raw data

```{r}
merged.df <- callFunction(
  "mainLabelsAndFactors",
  "Apply labels and create factors for main REDCap dataset",
  merged.df
)

nolabel <- names(merged.df)[lapply(merged.df, function(x) label(x)) == ""]

format_metadata <- function(data) {
  data %>%
    dplyr::select(
      one_of(
        c("field_name", "field_type", "field_label", "select_choices_or_calculations")
      )
    ) %>%
    dplyr::mutate(
      field_name = gsub("\\_", "\\.", field_name)
    )
}

labels.0 <- lapply(MAPfreeze.list[["epoch_0"]][["metadata"]][c("eligibility", "apoe")], format_metadata) %>% bind_rows()
labels.1 <- lapply(MAPfreeze.list[["epoch_1"]][["metadata"]][c("main", "cardiac.mri", "man3T", "man3T.bh", "auto3T", "auto3T.bh", "csf", "biomarkers", "srt", "addendum")], format_metadata) %>% bind_rows()
labels.2 <- lapply(MAPfreeze.list[["epoch_2"]][["metadata"]], format_metadata) %>% bind_rows()
labels.3 <- lapply(MAPfreeze.list[["epoch_3"]][["metadata"]], format_metadata) %>% bind_rows()
labels.4 <- lapply(MAPfreeze.list[["epoch_4"]][["metadata"]], format_metadata) %>% bind_rows()

labels.all <- dplyr::bind_rows(labels.0, labels.1, labels.2, labels.3, labels.4) %>% 
  dplyr::distinct() %>%
  dplyr::filter(field_name %in% nolabel)

duplicated.names <- labels.all$field_name[duplicated(labels.all$field_name)]

labels.all %<>%
  group_by(field_name) %>%
  arrange(field_name) %>%
  slice(1)

# labels.all <- filter(labels.all, field_name %nin% duplicated.names)

for (varname in labels.all$field_name) {
  Hmisc::label(merged.df[, varname]) <- labels.all[labels.all$field_name == varname, "field_label", drop = TRUE] %>%
    pull()
}

label(merged.df$epoch) <- "Epoch"

# Variables still without labels: grep("bHold", names(merged.df)[lapply(merged.df, function(x) label(x)) == ""], v = T, invert = T)
```

# Derivation of New Variables

## Dates #CHECK

```{r derive-dates}
merged.df <- callFunction("dates", "Convert dates", merged.df)
merged.df <- callFunction("datesDerived", "Derive date variables", merged.df)

merged.df %<>%
  mutate(
    abp.date = ifelse(abp.date == "1111-11-11", NA, abp.date),
    abp.date = as.Date(abp.date)
  )
```

## Demographics

```{r derive-demographic}
merged.df <- callFunction("demog", "Derive demographic variables", merged.df)
```

## APOE

```{r derive-apoe}
merged.df <- callFunction("apoe", "Derive APOE variables", merged.df)
```

## Medication and Surgery

```{r derive-medicationsAndSurgery}
merged.df <- callFunction(
  "medicationAndSurgery",  "Derive medication and surgery variables", merged.df,
  diabFile                        = MAPfreeze.list$epoch_0$data$diabetes.static,
  cholFile                        = MAPfreeze.list$epoch_0$data$cholesterol.static,
  #antihypFile                    = antihypFile, # changed processing 07 Oct 2016
  afibFile                        = MAPfreeze.list$epoch_0$data$afib.static,
  afibsurgFile                    = MAPfreeze.list$epoch_0$data$afibsurg.static,
  antihypBetaBlockerFile          = MAPfreeze.list$epoch_0$data$antihypBetaBlocker.static,
  antihypBetaBlockerIfNotDropFile = MAPfreeze.list$epoch_0$data$antihypBetaBlockerIfNotDrop.static,
  antihypACEInhibFile             = MAPfreeze.list$epoch_0$data$antihypACEInhib.static,
  antihypARBFile                  = MAPfreeze.list$epoch_0$data$antihypARB.static,
  antihypCCBFile                  = MAPfreeze.list$epoch_0$data$antihypCCB.static,
  antihypKSDFile                  = MAPfreeze.list$epoch_0$data$antihypKSD.static,
  antihypOtherFile                = MAPfreeze.list$epoch_0$data$antihypOther.static
)
```

## Blood Values

```{r derive-bloodConversion}
merged.df <- callFunction("bloodConversion", "Convert blood values", merged.df)
```

## Medical History

```{r derive-medhxEtc}
cmr.findings.rhythm.afib <- c(
  "atrial fibrillation"
)

cmr.findings.rhythm.normal <- c(
  "sinus"                                                ,
  "sinus with frequent pvcs"                             ,
  "sinus with frequent pvcs,"                            ,
  "sinus with atrial bigeminy"                           ,
  "sinus with frequent pacs"                             ,
  "sinus arrhythmia"                                     ,
  "sinus with intermittent second degree av block"       ,
  "sinus with frequent pvcs (often in trigeminy)"        ,
  "small"                                                ,
  "sinus with ivcd"                                      ,
  "sinus with frequent pvcs often in a trigeminy pattern"
)

merged.df <- callFunction("medhxEtc", "Derive medical history variables, etc.", merged.df)
```

## Cardiac Structure

```{r derive-cardiacStructure}
merged.df <- callFunction("cardiacStructure", "Derive a few echo variables", merged.df)
```

## ABP QC

```{r derive-abpqc}
merged.df <- callFunction("derive_abp_qc", "Derive ABP QC variables", merged.df)
```

## FSRP

```{r derive-fsrp}
merged.df <- callFunction("fsrp", "Derive FSRP", merged.df)
```

## Cognitive Complaint, FCADL, and FAQ

```{r derive-cognitiveComplaint}
merged.df <- callFunction("cognitiveComplaint", "Derive Cognitive Complaint, FCADL, and FAQ variables", merged.df)
```

## Neuropsych

```{r derive-neuropsych}
merged.df <- callFunction("neuropsych", "Derive neuropsych variables", merged.df)
```

## Addendum

```{r derive-addendum}
merged.df <- callFunction("addendum", "Label addendum variables and create a few factor variables", merged.df)
```

## MLTA and CHAMPS

```{r derive-mltaChamps}
merged.df <- callFunction("mltaChamps", "Derive MLTA and CHAMPS variables", merged.df)
```

## Depression

```{r derive-depression}
merged.df <- callFunction("depression", "Derive depression variables", merged.df)
```

## Biomarkers

```{r derive-biomarkers}
merged.df <- callFunction("biomarkers", "Derive biomarker (csf and other) variables", merged.df)
```

## Informant Information

```{r derive-informatInfo}
merged.df <- callFunction("informantInfo", "Derive informant information variables", merged.df)
```

## Automated 3T

```{r derive-auto3T}
merged.df <- callFunction("automated3T", "Derive automated 3T variables", merged.df)
```

## Manual 3T

```{r derive-man3T}
merged.df <- callFunction("manual3T", "Derive manual 3T variables", merged.df)
```

## Diagnosis and Staging

```{r derive-diagnosisAndStaging}
merged.df <- callFunction("diagnosisAndStaging", "Derive diagnosis and staging variables", merged.df)
```

## PSQI

```{r derive-psqi}
merged.df <- callFunction("psqi", "Derive PSQI variables", merged.df)
```

## Frailty

```{r derive-frailty}
merged.df <- callFunction("frailty", "Derive frailty variables", merged.df)
```

## Food Scan

```{r derive-foodScan}
merged.df <- callFunction("foodScan", "Derive food scan variables", merged.df)
```

## CMR and QMass

```{r derive-cardiacMRI}
merged.df <- callFunction("cardiacMRI", "Process CMR and QMass variables", merged.df)
```

## PVLT

```{r derive-pvlt}
merged.df <- callFunction("pvlt", "Process PVLT variables", merged.df)
```

# Set invalid values to missing

```{r}
merged.df <- callFunction("invalidNeuropsychElig", "Set invalid eligibility neuropsych items to missing", merged.df)
merged.df <- callFunction("invalidNeuropsychAddendum", "Set invalid neuropsych items from Addendum to missing", merged.df)
merged.df <- callFunction("invalidNeuropsychItems", "Set invalid neuropsych items from main protocol to missing", merged.df)
merged.df <- callFunction("invalidColorblind", "Set invalid colorblindness-related items to missing", merged.df)

# OAK 20180816: What about invalidCmr????
```

# Add baseline versions of certain variables onto every row

```{r repeatBaseline}
enrollmentVarsThatShouldNotChange <- Cs(
  dob,
  education,
  sex.factor,
  raceethnicity.factor,
  usa.born.factor,
  lang.prim.factor
)

otherKeyEnrollmentVars <- Cs(
  mci.stage.factor, 
  albert.mci.stage.factor, 
  age
)

epoch1ToRepeat <- merged.df[merged.df$epoch %in% 1, c('map.id', 'diagnosis.factor', enrollmentVarsThatShouldNotChange, otherKeyEnrollmentVars)]

for (vname in otherKeyEnrollmentVars) {
  label(epoch1ToRepeat[[vname]]) <- paste0(label(epoch1ToRepeat[[vname]]), ", from Enrollment")
}

names(epoch1ToRepeat) <- c("map.id", "enrolled.dx.factor", 
                           paste0("enrolled.", c(enrollmentVarsThatShouldNotChange, otherKeyEnrollmentVars)))

merged.df %<>% left_join(
  epoch1ToRepeat,
  by = "map.id"
)
```

The following variables were added to each row:

```{r}
data.frame(Variable = setdiff(names(epoch1ToRepeat), "map.id"))
```

# Add Memory and Executive Function Composite Scores

```{r}
composite.file <- file.path(
  data.raw.dir,
  'Mem_Ef_scores_9-29.csv'
)

composite.df <- read.csv(
  composite.file, 
  header = TRUE
)

colnames(composite.df) <- c("map.id", "epoch", "np.executive.composite", "np.memory.composite")
composite.df$map.id <- formatC(composite.df$map.id, width = 3, format = "d", flag = "0")

label(composite.df$np.executive.composite) <- 'EF Composite'
label(composite.df$np.memory.composite) <- 'Memory Composite'

merged.df %<>% left_join(
  composite.df,
  by = c("map.id", "epoch")
)

# merged.df <- merge(merged.df, composite.df, by = c('map.id', 'epoch'), all.x = TRUE)

merged.df[merged.df$map.id == "209" & merged.df$epoch == 1, 'np.memory.composite'] <- NA
```

# The merged file

```{r, saveFinalFiles}
bHoldnames <- setdiff(names(merged.df)[grep("^bHold\\.", names(merged.df))], "bHold.scan.date")
bHoldIndices <- match(bHoldnames, names(merged.df))

bHoldnamesWithCounterparts.temp <- bHoldnames[!(bHoldnames %in% c("bHold.session.id.11", "bHold.scan.date.11"))]
regnames.temp <- gsub("^bHold\\.", "", bHoldnamesWithCounterparts.temp)
regnames <- regnames.temp[regnames.temp %in% names(merged.df)] # Identify counterpart that are actually in alldat
bHoldnamesWithCounterparts <- bHoldnamesWithCounterparts.temp[regnames.temp %in% names(merged.df)]
reglabels <- label(merged.df[, regnames])

merged.fm.df <- merged.df[, -bHoldIndices]

merged.bh.df <- merged.df
merged.bh.df[merged.df$epoch == 1 & as.numeric(merged.df$map.id) <= 25, regnames] <- merged.bh.df[merged.df$epoch == 1 & as.numeric(merged.df$map.id) <= 25, bHoldnamesWithCounterparts]
merged.bh.df <- merged.bh.df[, -bHoldIndices]

# Add AD signatures
merged.fm.df <- derive_AD_sig(merged.fm.df)
merged.bh.df <- derive_AD_sig(merged.bh.df)

# Save the files in two formats.
saveRDS(merged.fm.df, file = paste0(data.merge.fm.file, ".rds"))
write.csv(merged.fm.df, file = paste0(data.merge.fm.file, ".csv"), row.names = FALSE)

saveRDS(merged.bh.df, file = paste0(data.merge.bh.file, ".rds"))
write.csv(merged.bh.df, file = paste0(data.merge.bh.file, ".csv"), row.names = FALSE)
```

<!-- Add code for daff function. -->
